Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
adding a comment.
Add a reply
adding cucumber book.

@@

\begin{quote}
    TBD: add ``The Cucumber Book'' to the bibliography as {\tt
    cucumber-book}.
\end{quote}

Cucumber~\cite{cucumber-book} is a higher-level approach to BDD for Ruby, and
it is typically used in combination with RSpec.
It focuses on user stories, to assist the developer in delivering
value to the stakeholder.
There is nothing comparable to Cucumber for Haskell, yet.  And we think
it would be interesting to explore, whether it is possible to apply
Cucumber's approach to BDD to Haskell.

>>>>

\begin{quote}
kazu: I guess ``Doctest integrated with QuickCheck'' is better.
\end{quote}

@@

Cucumber~\cite{cucumber} is a higher-level approach to BDD for Ruby, and
it is typically used in combination with RSpec.
It focuses on user stories, to assist the developer in delivering
value to the stakeholder.
There is nothing comparable to Cucumber for Haskell, yet.  And we think
it would be interesting to explore, whether it is possible to apply
Cucumber's approach to BDD to Haskell.
